The 2- and 3-point surface correlation functions calculations: from novel exact continuous approach to improving methodology for discrete images

### 2023-05-17 paper.tex
final (hopefully) text changes from kg
Explain what F_{sv} means in the abstract

\bibliographystyle{elsarticle-num}

@@

\begin{abstract}
  Surface correlation functions are extremely useful descriptors of interfaces
  and in this role can be used in material science, rock and soil physics, food
  engineering and other numerous areas. However, their widespread usage was
  hampered by insufficiently robust computation methodologies.  In this
  contribution we elaborate on recent works in surface function evaluation and
  present a novel exact algorithm to compute $F_{ss}$ and $F_{sss}$ functions
  for smooth boundary sets without discretization. This allows us to test
  digital computational approach on geometries beyond those with analytical
  solutions. Moreover, we propose a better edge detection filter that allowed to
  improve the quality of surface correlation functions (both surface-surface and
  surface-void) assessment based on digital images. The code for continuous and
  discrete computational frameworks is freely available and is now the part of
  the more general CorrelationFunctions.jl package.
\end{abstract}

>>>>

\bibliographystyle{elsarticle-num}
\journal{Physica A: Statistical Mechanics and its Applications}

@@

\begin{abstract}
  Surface correlation functions are extremely useful descriptors of interfaces
  and in this role can be used in material science, rock and soil physics, food
  engineering and other numerous areas. However, their widespread usage was
  hampered by insufficiently robust computation methodologies. In this
  contribution we elaborate on recent works in surface function evaluation and
  present a novel exact algorithm to compute surface-surface ($F_{ss}$) and
  surface-surface-surface ($F_{sss}$) functions for smooth boundary sets without
  discretization. This allows us to test digital computational approach on
  geometries beyond those available as analytical solutions. Moreover, we
  propose a better edge detection filter that allowed to improve the quality of
  assessment of surface correlation functions, both surface-surface and
  surface-void ($F_{sv}$), for digital images. The code for continuous and
  discrete computational frameworks is freely available and is now the part of
  the more general CorrelationFunctions.jl package.
\end{abstract}
